Finite Property Convex Elicitation Paper

### 2019-01-25 cvx-fin.tex
Fixing prop 8

	The following are equivalent:
	\begin{enumerate}
		\item $\Gamma$ embeds a finite elicitable property $\gamma:\simplex \toto \R$.
		\item The set $\{\Gamma_r : r \in \R \}$ is finite.
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$ that union to $\simplex$.
	\end{enumerate}
\end{proposition}
\begin{proof}
For $1 \implies 2$, by definition, if $\gamma$ is finite, then $\R$ is finite.
Thus, the set generated by indexing a finite set is finite.
For $2 \implies 3$, assume each level set $\Gamma_r$ in the given set is full-dimensional without loss of generality...
\jessie{TODO}

For $3 \implies 1$, observe that for each level set $\theta \in \Theta$, there is a report $u \in \reals^d$ such that $\Gamma_u = \theta$.
Let $\R$ be the collection of such reports $u$ corresponding to each level set.
The property $\gamma:p\mapsto \Gamma(p) \cap \R$ is then finite and embedded by $\Gamma$.
To see $\gamma$ is elicitable, consider that each level set of $\gamma$ is also a level set of $\Gamma$, and is therefore convex by the elicitability of $\Gamma$.
Since each level set is convex, we know $\gamma$ is elicitable.
\jessie{Cite?}
\end{proof}

>>>>

	The following are equivalent:
	\begin{enumerate}
		\item $\Gamma$ embeds a finite elicitable property $\gamma:\simplex \toto \R$.
		\item The set $\{\Gamma_r : r \in \R \}$ is finite.
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$ that union to $\simplex$.
	\end{enumerate}
\end{proposition}
\begin{proof}
For $1 \implies 2$, by definition, if $\gamma$ is finite, then $\R$ is finite.
Thus, the set $\Theta$ generated by indexing a finite set is finite.
For $2 \implies 3$, if any level set is not full-dimensional, it is the subset of a full-dimensional level set, so we can remove it while keeping the property nondegenerate.
Thus, this set $\Theta$ is still finite, consists of full-dimensional level sets, and unions to $\simplex$

For $3 \implies 1$, observe that for each level set $\theta \in \Theta$, there is a report $u \in \reals^d$ such that $\Gamma_u = \theta$.
Let $\R$ be the collection of such reports $u$ corresponding to each $\theta$.
The property $\gamma:p\mapsto \Gamma(p) \cap \R$ is then finite and embedded by $\Gamma$.
To see $\gamma$ is elicitable, consider that each level set of $\gamma$ is also a level set of $\Gamma$, and is therefore convex by the elicitability of $\Gamma$.
Since each level set is convex, we know $\gamma$ is elicitable.
\jessie{Cite?}
\end{proof}
